---
title: "Thesis Charts: Using Weighting Algorithms to Reduce Bad-Actor Reporting"
author: "Lucas Yang a.k.a. Ari Yang"
date: "2023-3-12"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Charts to Make

Chart 1: Removed malicious posts per algorithm per iteration (total)
Chart 2: Percentage malicious posts removed per algorithm per iteration (total) 
Chart 3: Percentage removed non-malicious posts per algorithm per iteration (total)
Pie Charts: Percentage of bad actor posts reported, percentage of good actor posts reported (maybe don't do)
Chart 4: Good and bad actor report ratings over time, smart 1 algorithm
Chart 5: Good and bad actor report ratings over time, smart 2 algorithm

## Reading the data file

First we need to read all of the data that we will be using for analysis.

```{r}
iteration1PostPath = "D:\\Schoolwork\\Thesis\\Data_files\\iteration1_posts.csv"
iteration1UserPath = "D:\\Schoolwork\\Thesis\\Data_files\\iteration1_users.csv"
iteration2PostPath = "D:\\Schoolwork\\Thesis\\Data_files\\iteration2_posts.csv"
iteration2UserPath = "D:\\Schoolwork\\Thesis\\Data_files\\iteration2_users.csv"
iteration3PostPath = "D:\\Schoolwork\\Thesis\\Data_files\\iteration3_posts.csv"
iteration3UserPath = "D:\\Schoolwork\\Thesis\\Data_files\\iteration3_users.csv"
iteration4PostPath = "D:\\Schoolwork\\Thesis\\Data_files\\iteration4_posts.csv"
iteration4UserPath = "D:\\Schoolwork\\Thesis\\Data_files\\iteration4_users.csv"
iteration5PostPath = "D:\\Schoolwork\\Thesis\\Data_files\\iteration5_posts.csv"
iteration5UserPath = "D:\\Schoolwork\\Thesis\\Data_files\\iteration5_users.csv"

Iteration1Posts <- read.csv(iteration1PostPath, header = TRUE)
Iteration1Users <- read.csv(iteration1UserPath, header = TRUE)
Iteration2Posts <- read.csv(iteration2PostPath, header = TRUE)
Iteration2Users <- read.csv(iteration2UserPath, header = TRUE)
Iteration3Posts <- read.csv(iteration3PostPath, header = TRUE)
Iteration3Users <- read.csv(iteration3UserPath, header = TRUE)
Iteration4Posts <- read.csv(iteration4PostPath, header = TRUE)
Iteration4Users <- read.csv(iteration4UserPath, header = TRUE)
Iteration5Posts <- read.csv(iteration5PostPath, header = TRUE)
Iteration5Users <- read.csv(iteration5UserPath, header = TRUE)
```

## Importing Libraries

In order to represent data in the best manner, this project will make use of the ggplot2 and tidyverse libraries to plot all the data. 

```{r}
library(ggplot2)
library(tidyverse)
```

# Data Overview

First, we will get familiar with the data sets which we imported.

```{r}
summary(Iteration5Users)
```
Data shows off the users, and how their values are distributed. 

```{r}
summary(Iteration5Posts) 
```
This data shows the posts, as well as the number of reports each post received. 

# Data Exploration 1: Removed malicious posts per algorithm per iteration (total)


```{r}
Iteration1MaliciousPosts <- subset(Iteration1Posts, Malicious == "true")
Iteration2MaliciousPosts <- subset(Iteration2Posts, Malicious == "true")
Iteration3MaliciousPosts <- subset(Iteration3Posts, Malicious == "true")
Iteration4MaliciousPosts <- subset(Iteration4Posts, Malicious == "true")
Iteration5MaliciousPosts <- subset(Iteration5Posts, Malicious == "true")

Dumb1MaliciousIterations = data.frame(NumRemoved = c(table(Iteration1MaliciousPosts$Dumb1Removed)["true"],
                  table(Iteration2MaliciousPosts$Dumb1Removed)["true"],
                  table(Iteration3MaliciousPosts$Dumb1Removed)["true"],
                  table(Iteration4MaliciousPosts$Dumb1Removed)["true"],
                  table(Iteration5MaliciousPosts$Dumb1Removed)["true"]), Iteration = 1:5)
Dumb2MaliciousIterations = data.frame(NumRemoved = c(table(Iteration1MaliciousPosts$Dumb2Removed)["true"],
                  table(Iteration2MaliciousPosts$Dumb2Removed)["true"],
                  table(Iteration3MaliciousPosts$Dumb2Removed)["true"],
                  table(Iteration4MaliciousPosts$Dumb2Removed)["true"],
                  table(Iteration5MaliciousPosts$Dumb2Removed)["true"]), Iteration = 1:5)
Smart1MaliciousIterations = data.frame(NumRemoved = c(table(Iteration1MaliciousPosts$Smart1Removed)["true"],
                  table(Iteration2MaliciousPosts$Smart1Removed)["true"],
                  table(Iteration3MaliciousPosts$Smart1Removed)["true"],
                  table(Iteration4MaliciousPosts$Smart1Removed)["true"],
                  table(Iteration5MaliciousPosts$Smart1Removed)["true"]), Iteration = 1:5)
Smart2MaliciousIterations = data.frame(NumRemoved = c(table(Iteration1MaliciousPosts$Smart2Removed)["true"],
                  table(Iteration2MaliciousPosts$Smart2Removed)["true"],
                  table(Iteration3MaliciousPosts$Smart2Removed)["true"],
                  table(Iteration4MaliciousPosts$Smart2Removed)["true"],
                  table(Iteration5MaliciousPosts$Smart2Removed)["true"]), Iteration = 1:5)

maliciousPostCount <- table(Iteration1Posts$Malicious)["true"]

plot(
  Dumb1MaliciousIterations$Iteration, Dumb1MaliciousIterations$NumRemoved,
  col = "red",
  type = 'l',
  main = "Cumulative Malicious Post Removal",
  xlab = "Iteration",
  ylab = "Malicious Posts Removed (Count)",
  ylim = c(0, maliciousPostCount)
)

lines(
  Dumb2MaliciousIterations$Iteration, Dumb2MaliciousIterations$NumRemoved,
  col = "blue",
  type = 'l'
)
lines(
  Smart1MaliciousIterations$Iteration, Smart1MaliciousIterations$NumRemoved,
  col = "green",
  type = 'l'
)
lines(
  Smart2MaliciousIterations$Iteration, Smart2MaliciousIterations$NumRemoved,
  col = "purple",
  type = 'l'
)

legend(
  1, 160000,
  legend = c("Dumb 1", "Dumb 2", "Smart 1", "Smart 2"),
  fill = c("red", "blue", "green", "purple")
)

par(new = TRUE)

plot(
  Dumb1MaliciousIterations$Iteration, (Dumb1MaliciousIterations$NumRemoved/maliciousPostCount)*100,
  col = "red",
  type = 'n',
  # main = "Cumulative Malicious Post Removal",
  # xlab = "Iteration",
  xlab = "",
  # ylab = "Malicious Posts Removed (%)",
  ylab = "",
  ylim = c(0, 100),
  yaxt = 'n'
)

axis(4)

```


## Data Exploration 2: Removed malicious posts per algorithm per iteration (percentage total)



```{r}
plot(
  Dumb1MaliciousIterations$Iteration, (Dumb1MaliciousIterations$NumRemoved/maliciousPostCount)*100,
  col = "red",
  type = 'l',
  main = "Cumulative Malicious Post Removal",
  xlab = "Iteration",
  ylab = "Malicious Posts Removed (%)",
  ylim = c(0, 100)
)

lines(
  Dumb2MaliciousIterations$Iteration, (Dumb2MaliciousIterations$NumRemoved/maliciousPostCount)*100,
  col = "blue",
  type = 'l'
)
lines(
  Smart1MaliciousIterations$Iteration, (Smart1MaliciousIterations$NumRemoved/maliciousPostCount)*100,
  col = "green",
  type = 'l'
)
lines(
  Smart2MaliciousIterations$Iteration, (Smart2MaliciousIterations$NumRemoved/maliciousPostCount)*100,
  col = "purple",
  type = 'l'
)

legend(
  1, 95,
  legend = c("Dumb 1", "Dumb 2", "Smart 1", "Smart 2"),
  fill = c("red", "blue", "green", "purple")
)

(Dumb1MaliciousIterations$NumRemoved/maliciousPostCount)*100
(Dumb2MaliciousIterations$NumRemoved/maliciousPostCount)*100
(Smart1MaliciousIterations$NumRemoved/maliciousPostCount)*100
(Smart2MaliciousIterations$NumRemoved/maliciousPostCount)*100
```


## Data Exploration 3: Removed non-malicious posts per algorithm per iteration (percentage total)

```{r}
Iteration1NonMaliciousPosts <- subset(Iteration1Posts, Malicious == "false")
Iteration2NonMaliciousPosts <- subset(Iteration2Posts, Malicious == "false")
Iteration3NonMaliciousPosts <- subset(Iteration3Posts, Malicious == "false")
Iteration4NonMaliciousPosts <- subset(Iteration4Posts, Malicious == "false")
Iteration5NonMaliciousPosts <- subset(Iteration5Posts, Malicious == "false")

Dumb1NonMaliciousIterations = data.frame(NumRemoved = c(table(Iteration1NonMaliciousPosts$Dumb1Removed)["true"],
                  table(Iteration2NonMaliciousPosts$Dumb1Removed)["true"],
                  table(Iteration3NonMaliciousPosts$Dumb1Removed)["true"],
                  table(Iteration4NonMaliciousPosts$Dumb1Removed)["true"],
                  table(Iteration5NonMaliciousPosts$Dumb1Removed)["true"]), Iteration = 1:5)
Dumb2NonMaliciousIterations = data.frame(NumRemoved = c(table(Iteration1NonMaliciousPosts$Dumb2Removed)["true"],
                  table(Iteration2NonMaliciousPosts$Dumb2Removed)["true"],
                  table(Iteration3NonMaliciousPosts$Dumb2Removed)["true"],
                  table(Iteration4NonMaliciousPosts$Dumb2Removed)["true"],
                  table(Iteration5NonMaliciousPosts$Dumb2Removed)["true"]), Iteration = 1:5)
Smart1NonMaliciousIterations = data.frame(NumRemoved = c(table(Iteration1NonMaliciousPosts$Smart1Removed)["true"],
                  table(Iteration2NonMaliciousPosts$Smart1Removed)["true"],
                  table(Iteration3NonMaliciousPosts$Smart1Removed)["true"],
                  table(Iteration4NonMaliciousPosts$Smart1Removed)["true"],
                  table(Iteration5NonMaliciousPosts$Smart1Removed)["true"]), Iteration = 1:5)
Smart2NonMaliciousIterations = data.frame(NumRemoved = c(table(Iteration1NonMaliciousPosts$Smart2Removed)["true"],
                  table(Iteration2NonMaliciousPosts$Smart2Removed)["true"],
                  table(Iteration3NonMaliciousPosts$Smart2Removed)["true"],
                  table(Iteration4NonMaliciousPosts$Smart2Removed)["true"],
                  table(Iteration5NonMaliciousPosts$Smart2Removed)["true"]), Iteration = 1:5)

nonMaliciousPostCount <- table(Iteration1Posts$Malicious)["false"]

plot(
  Dumb1NonMaliciousIterations$Iteration, (Dumb1NonMaliciousIterations$NumRemoved/nonMaliciousPostCount)*100,
  col = "red",
  type = 'l',
  main = "Cumulative Non-Malicious Post Removal",
  xlab = "Iteration",
  ylab = "Non-Malicious Posts Removed (%)",
  ylim = c(0, 25)
)

lines(
  Dumb2NonMaliciousIterations$Iteration, (Dumb2NonMaliciousIterations$NumRemoved/nonMaliciousPostCount)*100,
  col = "blue",
  type = 'l'
)
lines(
  Smart1NonMaliciousIterations$Iteration, (Smart1NonMaliciousIterations$NumRemoved/nonMaliciousPostCount)*100,
  col = "green",
  type = 'l'
)
lines(
  Smart2NonMaliciousIterations$Iteration, (Smart2NonMaliciousIterations$NumRemoved/nonMaliciousPostCount)*100,
  col = "purple",
  type = 'l'
)

legend(
  4, 25,
  legend = c("Dumb 1", "Dumb 2", "Smart 1", "Smart 2"),
  fill = c("red", "blue", "green", "purple")
)

(Dumb1NonMaliciousIterations$NumRemoved/nonMaliciousPostCount)*100
(Dumb2NonMaliciousIterations$NumRemoved/nonMaliciousPostCount)*100
(Smart1NonMaliciousIterations$NumRemoved/nonMaliciousPostCount)*100
(Smart2NonMaliciousIterations$NumRemoved/nonMaliciousPostCount)*100

```


# Data Exploration 4: Good and bad actor report ratings over time, smart 1 algorithm


```{r}
Iteration1BadActors <- subset(Iteration1Users, BadActor == "true")
Iteration2BadActors <- subset(Iteration2Users, BadActor == "true")
Iteration3BadActors <- subset(Iteration3Users, BadActor == "true")
Iteration4BadActors <- subset(Iteration4Users, BadActor == "true")
Iteration5BadActors <- subset(Iteration5Users, BadActor == "true")

Iteration1GoodActors <- subset(Iteration1Users, BadActor == "false")
Iteration2GoodActors <- subset(Iteration2Users, BadActor == "false")
Iteration3GoodActors <- subset(Iteration3Users, BadActor == "false")
Iteration4GoodActors <- subset(Iteration4Users, BadActor == "false")
Iteration5GoodActors <- subset(Iteration5Users, BadActor == "false")

#Iteration1BadActors['Iteration']=1

Smart1BadActorRatings = data.frame(AvgRating = c(mean(Iteration1BadActors$Smart1Value),
                  mean(Iteration2BadActors$Smart1Value),
                  mean(Iteration3BadActors$Smart1Value),
                  mean(Iteration4BadActors$Smart1Value),
                  mean(Iteration5BadActors$Smart1Value)), Iteration = 1:5)
Smart1GoodActorRatings = data.frame(AvgRating = c(mean(Iteration1GoodActors$Smart1Value),
                  mean(Iteration2GoodActors$Smart1Value),
                  mean(Iteration3GoodActors$Smart1Value),
                  mean(Iteration4GoodActors$Smart1Value),
                  mean(Iteration5GoodActors$Smart1Value)), Iteration = 1:5)

plot(
  Smart1BadActorRatings$Iteration, Smart1BadActorRatings$AvgRating,
  col = "red",
  main = "Average User Report Rating Within the Smart 1 Algorithm",
  xlab = "Iteration",
  ylab = "Score",
  type = 'l',
  xlim = c(1, 5),
  ylim = c(0, 3)
)

lines(
  Smart1BadActorRatings$Iteration, Smart1BadActorRatings$AvgRating,
  type = 'o',
  col = 'red'
)
lines(
  Smart1GoodActorRatings$Iteration, Smart1GoodActorRatings$AvgRating,
  type = 'l',
  col = 'blue'
)
lines(
  Smart1GoodActorRatings$Iteration, Smart1GoodActorRatings$AvgRating,
  type = 'o',
  col = 'blue'
)

legend(
  1, 3,
  legend = c("Bad Actors", "Good Actors"),
  fill = c("red", "blue")
)
```

# Data Exploration 4: Good and bad actor report ratings over time, smart 2 algorithm

```{r}
Smart2BadActorRatings = data.frame(AvgRating = c(mean(Iteration1BadActors$Smart2Value),
                  mean(Iteration2BadActors$Smart2Value),
                  mean(Iteration3BadActors$Smart2Value),
                  mean(Iteration4BadActors$Smart2Value),
                  mean(Iteration5BadActors$Smart2Value)), Iteration = 1:5)
Smart2GoodActorRatings = data.frame(AvgRating = c(mean(Iteration1GoodActors$Smart2Value),
                  mean(Iteration2GoodActors$Smart2Value),
                  mean(Iteration3GoodActors$Smart2Value),
                  mean(Iteration4GoodActors$Smart2Value),
                  mean(Iteration5GoodActors$Smart2Value)), Iteration = 1:5)

plot(
  Smart2BadActorRatings$Iteration, Smart2BadActorRatings$AvgRating,
  col = "red",
  main = "Average User Report Rating Within the Smart 2 Algorithm",
  xlab = "Iteration",
  ylab = "Score",
  type = 'l',
  xlim = c(1, 5),
  ylim = c(0, 3)
)

lines(
  Smart2BadActorRatings$Iteration, Smart2BadActorRatings$AvgRating,
  type = 'o',
  col = 'red'
)
lines(
  Smart2GoodActorRatings$Iteration, Smart2GoodActorRatings$AvgRating,
  type = 'l',
  col = 'blue'
)
lines(
  Smart2GoodActorRatings$Iteration, Smart2GoodActorRatings$AvgRating,
  type = 'o',
  col = 'blue'
)

legend(
  1, 3,
  legend = c("Bad Actors", "Good Actors"),
  fill = c("red", "blue")
)
```

